---
title: "Neighborhood Report"
execute:
  echo: false
  message: false
  warning: false
format: 
  html:
    embed-resources: false
editor: visual
---

```{r}
#| echo: false
#| message: false
#| warning: false

## Housekeeping

## ---------------------------
## libraries
## ---------------------------
library(tidyverse)
library(readxl)
library(openxlsx)
library(janitor)
library(kableExtra)
library(pwr)
library(kableExtra)
library(knitr)

## ---------------------------
## directory paths
## ---------------------------

#see current directory
#getwd()

#set current directory
code_file_dir<-file.path("C:/Users/yjeff/Desktop/Community Schools/Teacher Retention Data",
                "Analyses", "cs_teach_rent2", "y3_data")

data_file_dir<-file.path("C:/Users/yjeff/Box/LAUSD TR Data Year 3")

## ---------------------------
## helper functions
## ---------------------------

update_tbl_names<-function(df){
  df_update<-df
  colnames(df_update)<-c("School", "2019", "2020", "2021", "2022", "2023")
  return(df_update)
}

## ---------------------------
## load & inspect data
## ---------------------------

load(file.path(code_file_dir, "rent_tbls.RData"))
load(file.path(code_file_dir, "rent_plots.RData"))

#toc tables
load(file.path(code_file_dir, "toc_rent_tbls.RData"))
load(file.path(code_file_dir, "rent_plots_toc.RData"))

load(file.path(code_file_dir, "hr_by_sch.RData"))
load(file.path(code_file_dir, "veteran_rent_tbls.RData"))
load(file.path(code_file_dir, "veteran_plots.RData"))

## Add Lists
source(file.path(code_file_dir, "00_school_lists.R"))

#Clean Original Tables
rent_by_neighborhood_toc<-map(rent_by_neighborhood_toc,
          function(neighborhood) map(neighborhood,
          function(a){
            update_df<-a %>% select(-c(rent))
            colnames(update_df)<-c('school', "2019",
                                   "2020","2021","2022","2023")
            return(update_df)
            }
          ))
```

## Purpose

The purpose of this document is to present neighborhood-specific retention rates. We begin with an overview, categorizing neighborhoods based on where community schools (CS) exhibit higher, mixed/neutral, or lower retention rates compared to traditional public schools (TS). Following the overview, we provide more details of the retention rates for each neighborhood.

## Overview

+--------------------------------------------------+---------------------------------------------------+-------------------------------------------------+
| Neighborhoods where CS have Higher Rates than TS | Neighborhoods where CS have Similar Rates than TS | Neighborhoods where CS have Lower Rates than TS |
+==================================================+===================================================+=================================================+
| 1.  LA Mid-City                                  | 1.  Hamilton                                      | 1.  Gardena                                     |
|                                                  | 2.  Monroe                                        | 2.  South LA                                    |
| 2.  HEET                                         | 3.  Bell Cudahy Maywood                           | 3.  Venice                                      |
|                                                  | 4.  Downtown                                      | 4.  Macarthur Park                              |
| 3.  Boyle Heights                                | 5.  Sun Valley                                    | 5.  Panorama City                               |
|                                                  | 6.  Riveria                                       |                                                 |
| 4.  Lincoln Heights El Sereno                    | 7.  Fremont                                       |                                                 |
|                                                  | 8.  Huntington Park/Vernon                        |                                                 |
| 5.  Van Nuys Valley Glen                         |                                                   |                                                 |
|                                                  |                                                   |                                                 |
| 6.  Hollywood                                    |                                                   |                                                 |
|                                                  |                                                   |                                                 |
| 7.  Carson                                       |                                                   |                                                 |
+--------------------------------------------------+---------------------------------------------------+-------------------------------------------------+
|                                                  |                                                   |                                                 |
+--------------------------------------------------+---------------------------------------------------+-------------------------------------------------+

## Neighborhoods where CS have Higher Retention Rates than TS

<details>

```{r, echo = FALSE, results='asis'}

neighborhood_string<-c("LA Mid-City", "Heet", "Boyle Heights",
                    "Lincoln Heights El Sereno",
                    "Van Nuys Valley Glen", "Hollywood", "Carson")

neighborhood_num<-which(update_neigh_string %in% neighborhood_string)

gxs<-lapply(1:length(neighborhood_string), function(x){
  
  neighborhood_title <- update_neigh_string[neighborhood_num][[x]]
  
  knit_child(
    '_03.4_report_full - child.Rmd', envir = environment(), quiet = TRUE
    
  )
  
})

cat(unlist(gxs), sep = '\n')

```

</details>

## Neighborhoods where CS have Similar Retention Rates than TS

<details>

```{r, echo = FALSE, results='asis'}

neighborhood_string<-c("Hamilton", "Monroe", "Bell Cudahy Maywood",
                    "Downtown", "Sun Valley", "Riveria",
                    "Fremont", "Huntington Park Vernon")

neighborhood_num<-which(update_neigh_string %in% neighborhood_string)

gxs<-lapply(1:length(neighborhood_string), function(x){
  
  neighborhood_title <- update_neigh_string[neighborhood_num][[x]]
  # neighborhood_df<-rent_by_neighborhood_toc
  # neighborhood<-names(rent_by_neighborhood)[neighborhood_num][[x]]
  # bar_plots_neigh_df<-bar_plots_neigh
  
  
  knit_child(
    '_03.4_report_full - child.Rmd', envir = environment(), quiet = TRUE
    
  )
  
})

cat(unlist(gxs), sep = '\n')

```

</details>

## Neighborhoods where CS have Lower Retention Rates than TS

<details>

```{r, echo = FALSE, results='asis'}

neighborhood_string<-c("Gardena", "South LA", "Venice",
                    "Macarthur Park", "Panorama City")

neighborhood_num<-which(update_neigh_string %in% neighborhood_string)

gxs<-lapply(1:length(neighborhood_string), function(x){
  
  neighborhood_title <- update_neigh_string[neighborhood_num][[x]]
  
  knit_child(
    '_03.4_report_full - child.Rmd', envir = environment(), quiet = TRUE
    
  )
  
})

cat(unlist(gxs), sep = '\n')

```

</details>
