---
title: "Teacher Veteran Status Report - Average Teacher Retention"
execute:
  echo: false
  message: false
  warning: false
format: 
  html:
    embed-resources: true
editor: visual
---

## Purpose

1.  Analyzes the teacher retention based on teacher veteran status. This is an updated version, which now looks at teacher veteran status across the following categories:
    -   0-3 Years
    -   4-5 Years
    -   6-10 Years
    -   11-15 Years
    -   Over 15 Years


## Calculation

Rates shown here are the average teacher retention rate across schools. These rates are calculated by taking the retention rate of each school and dividing it by the number of schools in the sample. If there are cases where, in a school cell, there are no teachers, then that school is not included in the average calculation. 

```{r}
#| echo: false
#| message: false
#| warning: false

## Housekeeping

## ---------------------------
## libraries
## ---------------------------
library(tidyverse)
library(readxl)
library(openxlsx)
library(janitor)
library(kableExtra)
library(pwr)
library(kableExtra)
library(knitr)

## ---------------------------
## directory paths
## ---------------------------

#see current directory
#getwd()

#set current directory
code_file_dir<-file.path("C:/Users/yjeff/Desktop/Community Schools/Teacher Retention Data","Analyses", "cs_teach_rent2","y3_data")

data_file_dir<-file.path("C:/Users/yjeff/Box/LAUSD TR Data Year 3")

## ---------------------------
## helper functions
## ---------------------------

update_tbl_names<-function(df){
  df_update<-df
  colnames(df_update)<-c("School", "2019", "2020", "2021", "2022", "2023")
  return(df_update)
}

## ---------------------------
## load & inspect data
## ---------------------------

load(file.path(code_file_dir, "veteran_rent_tbls.RData"))
load(file.path(code_file_dir, "veteran_plots.RData"))

## Add Lists
source(file.path(code_file_dir, "00_school_lists.R"))


```

# Descriptive Analyses - Retention Rates

## All Schools

<details>
```{r, echo = FALSE, results='asis'}
teach_yr_string<-names(toc_rent_overall[["ts"]][["original_5"]])


gxs<-lapply(1:length(teach_yr_string), function(x){
  
  teach_year <- teach_yr_string[[x]]
  type<-"overall"
  df_cs<-toc_rent_overall2[["cs"]][["original_5"]][[teach_year]]
  df_ts<-toc_rent_overall2[["ts"]][["original_5"]][[teach_year]]
  
  #neighborhood<-names(rent_by_neighborhood)[[x]]

  knit_child(
    '_06_report_full - child.Rmd', envir = environment(), quiet = TRUE
    
  )
  
})

cat(unlist(gxs), sep = '\n')

```

</details>

## Elementary Schools

<details>
```{r, echo = FALSE, results='asis'}
teach_yr_string<-names(toc_rent_overall[["ts"]][["original_5"]])


gxs<-lapply(1:length(teach_yr_string), function(x){
  
  teach_year <- teach_yr_string[[x]]
  type<-"elem"
  df_cs<-toc_rent_overall_elem2[["cs"]][["original_5"]][[teach_year]]
  df_ts<-toc_rent_overall_elem2[["ts"]][["original_5"]][[teach_year]]
  
  #neighborhood<-names(rent_by_neighborhood)[[x]]

  knit_child(
    '_06_report_full - child.Rmd', envir = environment(), quiet = TRUE
    
  )
  
})

cat(unlist(gxs), sep = '\n')

```

</details>

## Middle/High Schools

<details>
```{r, echo = FALSE, results='asis'}
teach_yr_string<-names(toc_rent_overall[["ts"]][["original_5"]])


gxs<-lapply(1:length(teach_yr_string), function(x){
  
  teach_year <- teach_yr_string[[x]]
  type<-"ms_hs"
  df_cs<-toc_rent_overall_ms_hs2[["cs"]][["original_5"]][[teach_year]]
  df_ts<-toc_rent_overall_ms_hs2[["ts"]][["original_5"]][[teach_year]]
  
  #neighborhood<-names(rent_by_neighborhood)[[x]]

  knit_child(
    '_06_report_full - child.Rmd', envir = environment(), quiet = TRUE
    
  )
  
})

cat(unlist(gxs), sep = '\n')

```

</details>

