---
title: "Test Results"
execute:
  echo: false
  message: false
  warning: false
format: 
  html:
    embed-resources: true
editor: visual
---

```{r}
#| echo: false
#| message: false
#| warning: false

## Housekeeping

## ---------------------------
## libraries
## ---------------------------
library(tidyverse)
library(readxl)
library(openxlsx)
library(janitor)
library(kableExtra)
library(pwr)
library(kableExtra)
library(knitr)

## ---------------------------
## directory paths
## ---------------------------

#see current directory
#getwd()

#set current directory
code_file_dir<-file.path("C:/Users/yjeff/Desktop/Community Schools/Teacher Retention Data",
                "Analyses","cs_teach_rent2",  "y3_data")

data_file_dir<-file.path("C:/Users/yjeff/Box/LAUSD TR Data Year 3")

## ---------------------------
## helper functions
## ---------------------------

update_tbl_names<-function(df){
  df_update<-df
  colnames(df_update)<-c("School", "2019", "2020", "2021", "2022", "2023")
  return(df_update)
}

## ---------------------------
## load & inspect data
## ---------------------------

# load(file.path(code_file_dir, "rent_tbls.RData"))
# load(file.path(code_file_dir, "rent_plots.RData"))

#toc tables
# load(file.path(code_file_dir, "toc_rent_tbls.RData"))
# load(file.path(code_file_dir, "rent_plots_toc.RData"))

load(file.path(code_file_dir, "test_tbls.RData"))


## Add Lists
source(file.path(code_file_dir, "00_school_lists.R"))


```

## Purpose

The purpose of this document is to show the test results comparing Community Schools with their Traditional Public Schools.

## T-Test Results

Notes: NA values are due to missing cases. For example, if a Community School does not have any 4-5 teachers for a given year, then running t-test results was not available.


### Overall
<details>
::: panel-tabset

#### Full

```{r, echo = FALSE, results='asis'}

t_test<-combined_t_test %>% 
  select(-c(conf_low, conf_high, statistic)) 

colnames(t_test)<-c('Neighborhood',"CS", "TS",
                    "Diff.", "p-value", "df")

t_test %>% kable()
```

#### Curated

```{r, echo = FALSE, results='asis'}

t_test<-combined_t_test %>% 
  select(-c(conf_low, conf_high, statistic)) 

colnames(t_test)<-c('Neighborhood',"CS", "TS",
                    "Diff.", "p-value", "df")

t_test<-t_test %>% 
  filter(`p-value`< 0.05) 

t_test %>% kable()
```

::: 
</details>

### 0-3 Years

<details>
::: panel-tabset

#### Full
```{r, echo = FALSE, results='asis'}

t_test<-combined_t_test_veteran[["original_5"]][["0-3 years"]] %>% 
  select(-c(conf_low, conf_high, statistic)) 

colnames(t_test)<-c('Neighborhood',"CS", "TS",
                    "Diff.", "p-value", "df")

t_test %>% kable()

```

#### Curated
```{r, echo = FALSE, results='asis'}

t_test<-combined_t_test_veteran[["original_5"]][["0-3 years"]] %>% 
  select(-c(conf_low, conf_high, statistic)) 

colnames(t_test)<-c('Neighborhood',"CS", "TS",
                    "Diff.", "p-value", "df")

t_test<-t_test %>% 
  filter(`p-value`< 0.05) 

t_test %>% kable()
```

:::
</details>

### 4-5 Years

<details>
::: panel-tabset
#### All
```{r, echo = FALSE, results='asis'}

t_test<-combined_t_test_veteran[["original_5"]][["4-5 years"]] %>% 
  select(-c(conf_low, conf_high, statistic)) 

colnames(t_test)<-c('Neighborhood',"CS", "TS",
                    "Diff.", "p-value", "df")

t_test %>% kable()

```

#### Curated
```{r, echo = FALSE, results='asis'}

t_test<-combined_t_test_veteran[["original_5"]][["4-5 years"]] %>% 
  select(-c(conf_low, conf_high, statistic)) 

colnames(t_test)<-c('Neighborhood',"CS", "TS",
                    "Diff.", "p-value", "df")

t_test<-t_test %>% 
  filter(`p-value`< 0.05) 

t_test %>% kable()
```
:::
</details>


### 6-10 Years

<details>
::: panel-tabset
#### All

```{r, echo = FALSE, results='asis'}

t_test<-combined_t_test_veteran[["original_5"]][["6-10 years"]] %>% 
  select(-c(conf_low, conf_high, statistic)) 

colnames(t_test)<-c('Neighborhood',"CS", "TS",
                    "Diff.", "p-value", "df")

t_test %>% kable()

```


#### Curated

```{r, echo = FALSE, results='asis'}

t_test<-combined_t_test_veteran[["original_5"]][["6-10 years"]] %>% 
  select(-c(conf_low, conf_high, statistic)) 

colnames(t_test)<-c('Neighborhood',"CS", "TS",
                    "Diff.", "p-value", "df")

t_test<-t_test %>% 
  filter(`p-value`< 0.05) 

t_test %>% kable()
```
:::

</details>

### 11-15 Years

<details>
::: panel-tabset
#### Full

```{r, echo = FALSE, results='asis'}

t_test<-combined_t_test_veteran[["original_5"]][["11-15 years"]] %>% 
  select(-c(conf_low, conf_high, statistic)) 

colnames(t_test)<-c('Neighborhood',"CS", "TS",
                    "Diff.", "p-value", "df")

t_test %>% kable()

```

#### Curated
```{r, echo = FALSE, results='asis'}

t_test<-combined_t_test_veteran[["original_5"]][["11-15 years"]] %>% 
  select(-c(conf_low, conf_high, statistic)) 

colnames(t_test)<-c('Neighborhood',"CS", "TS",
                    "Diff.", "p-value", "df")

t_test<-t_test %>% 
  filter(`p-value`< 0.05) 

t_test %>% kable()
```
:::

</details>

### 15+ Years

<details>
::: panel-tabset
#### Full

```{r, echo = FALSE, results='asis'}

t_test<-combined_t_test_veteran[["original_5"]][["15+ years"]] %>% 
  select(-c(conf_low, conf_high, statistic)) 

colnames(t_test)<-c('Neighborhood',"CS", "TS",
                    "Diff.", "p-value", "df")

t_test %>% kable()

```

#### Curated

```{r, echo = FALSE, results='asis'}

t_test<-combined_t_test_veteran[["original_5"]][["15+ years"]] %>% 
  select(-c(conf_low, conf_high, statistic)) 

colnames(t_test)<-c('Neighborhood',"CS", "TS",
                    "Diff.", "p-value", "df")

t_test<-t_test %>% 
  filter(`p-value`< 0.05) 

t_test %>% kable()
```
:::

</details>
