---
title: "CS Only School Report - By Cohort"
execute:
  echo: false
  message: false
  warning: false
format: 
  html:
    embed-resources: false
editor: visual
---

## Purpose

This is an update version of the CS Only School report. There are two updates:

1.  Retention rates are displayed exclusively for the period after schools became community schools, with data from years prior to this status excluded.

2.  Report also includes retention rates broken down by cohort.

```{r}
#| echo: false
#| message: false
#| warning: false

## Housekeeping

## ---------------------------
## libraries
## ---------------------------
library(tidyverse)
library(readxl)
library(openxlsx)
library(janitor)
library(kableExtra)
library(pwr)
library(kableExtra)
library(knitr)

## ---------------------------
## directory paths
## ---------------------------

#see current directory
#getwd()

#set current directory
code_file_dir<-file.path("C:/Users/yjeff/Desktop/Community Schools/Teacher Retention Data","Analyses", "cs_teach_rent2","y3_data")

data_file_dir<-file.path("C:/Users/yjeff/Box/LAUSD TR Data Year 3")

## ---------------------------
## helper functions
## ---------------------------

update_tbl_names<-function(df){
  df_update<-df
  colnames(df_update)<-c("School", "2019", "2020", "2021", "2022", "2023")
  return(df_update)
}

## ---------------------------
## load & inspect data
## ---------------------------

load(file.path(code_file_dir, "combined_cohort_rent_tbls.RData"))
load(file.path(code_file_dir, "by_cohort_plots.RData"))

## Add Lists
source(file.path(code_file_dir, "00_school_lists.R"))
```

# Descriptive Analyses - Retention Rates

## Combined Overall

Includes retention rates only from the time schools became community schools, excluding data from years prior to their community school status.

<details>

```{r, echo = FALSE, results='asis'}
teach_yr_string<-names(combined_overall_bp[["22_23"]])

gxs<-lapply(1:length(teach_yr_string), function(x){
  
  teach_year <- teach_yr_string[[x]]
  plot_list_22_23<-combined_overall_bp[["22_23"]]
  plot_list_all_years<-combined_overall_bp[["all_yrs"]]
  rent_tbl<-combined_overall_rent_tbls

  knit_child(
    '_07.3_report_full - child.Rmd', envir = environment(), quiet = TRUE
    
  )
})

cat(unlist(gxs), sep = '\n')

```

</details>

## By Cohort Analysis

### Cohort 1
<details>

```{r, echo = FALSE, results='asis'}
#overall Cohort
teach_yr_string<-c("overall")

gxs<-lapply(1:length(teach_yr_string), function(x){
  
  teach_year <- teach_yr_string[[x]]
  plot_list_22_23<-overall_bp[["22_23"]][["cohort_1"]]
  plot_list_all_years<-overall_bp[["all_yrs"]][["cohort_1"]]
  rent_tbl<-cohort_overall_v2[["cohort_1"]]
  
  knit_child(
    '_07.4_report_full - child.Rmd', envir = environment(), quiet = TRUE
    
  )
})

cat(unlist(gxs), sep = '\n')
```


```{r, echo = FALSE, results='asis'}
teach_yr_string<-names(cohort_bp[["22_23"]][["cohort_1"]])

gxs<-lapply(1:length(teach_yr_string), function(x){
  
  teach_year <- teach_yr_string[[x]]
  plot_list_22_23<-cohort_bp[["22_23"]][["cohort_1"]]
  plot_list_all_years<-cohort_bp[["all_yrs"]][["cohort_1"]]
  rent_tbl<-cohort_overall_teach_exp_v2[["cohort_1"]]    
  

  knit_child(
    '_07.3_report_full - child.Rmd', envir = environment(), quiet = TRUE
    
  )
})

cat(unlist(gxs), sep = '\n')
```

</details>

### Cohort 2

<details>

```{r, echo = FALSE, results='asis'}
#overall Cohort
teach_yr_string<-c("overall")

gxs<-lapply(1:length(teach_yr_string), function(x){
  
  teach_year <- teach_yr_string[[x]]
  plot_list_22_23<-overall_bp[["22_23"]][["cohort_2"]]
  plot_list_all_years<-overall_bp[["all_yrs"]][["cohort_2"]]
  rent_tbl<-cohort_overall_v2[["cohort_2"]]
  
  knit_child(
    '_07.4_report_full - child.Rmd', envir = environment(), quiet = TRUE
    
  )
})

cat(unlist(gxs), sep = '\n')
```

```{r, echo = FALSE, results='asis'}
teach_yr_string<-names(cohort_bp[["22_23"]][["cohort_2"]])

gxs<-lapply(1:length(teach_yr_string), function(x){
  
  teach_year <- teach_yr_string[[x]]
  plot_list_22_23<-cohort_bp[["22_23"]][["cohort_2"]]
  plot_list_all_years<-cohort_bp[["all_yrs"]][["cohort_2"]]
  rent_tbl<-cohort_overall_teach_exp_v2[["cohort_2"]]

  knit_child(
    '_07.3_report_full - child.Rmd', envir = environment(), quiet = TRUE
    
  )
})

cat(unlist(gxs), sep = '\n')
```

</details>

### Cohort 3

<details>

```{r, echo = FALSE, results='asis'}
#overall Cohort
teach_yr_string<-c("overall")

gxs<-lapply(1:length(teach_yr_string), function(x){
  
  teach_year <- teach_yr_string[[x]]
  plot_list_22_23<-overall_bp[["22_23"]][["cohort_3"]]
  plot_list_all_years<-overall_bp[["all_yrs"]][["cohort_3"]]
  rent_tbl<-cohort_overall_v2[["cohort_3"]]
  
  knit_child(
    '_07.4_report_full - child.Rmd', envir = environment(), quiet = TRUE
    
  )
})

cat(unlist(gxs), sep = '\n')
```


```{r, echo = FALSE, results='asis'}
teach_yr_string<-names(cohort_bp[["22_23"]][["cohort_3"]])

gxs<-lapply(1:length(teach_yr_string), function(x){
  
  teach_year <- teach_yr_string[[x]]
  plot_list_22_23<-cohort_bp[["22_23"]][["cohort_3"]]
  plot_list_all_years<-cohort_bp[["all_yrs"]][["cohort_3"]]
  rent_tbl<-cohort_overall_teach_exp_v2[["cohort_3"]]

  knit_child(
    '_07.3_report_full - child.Rmd', envir = environment(), quiet = TRUE
    
  )
})

cat(unlist(gxs), sep = '\n')
```

</details>


### Cohort by Cohort Comparison
<details>
```{r, echo = FALSE, results='asis'}
teach_yr_string<-c("Overall",
                   names(cohort_bp[["22_23"]][["cohort_3"]]))

gxs<-lapply(1:length(teach_yr_string), function(x){
  
  teach_year <- teach_yr_string[[x]]
  
  if (x == 1){
    cohort_1_plot<-
      overall_bp[["all_yrs"]][["cohort_1"]]
    cohort_2_plot<-
      overall_bp[["all_yrs"]][["cohort_2"]]
    cohort_3_plot<-
      overall_bp[["all_yrs"]][["cohort_3"]]
  }
  
  if (x >1){
    cohort_1_plot<-cohort_bp[["all_yrs"]][["cohort_1"]][[teach_year]]
    cohort_2_plot<-cohort_bp[["all_yrs"]][["cohort_2"]][[teach_year]]
    cohort_3_plot<-cohort_bp[["all_yrs"]][["cohort_3"]][[teach_year]]
  }
  
  knit_child(
    '_07.5_report_full - child.Rmd', envir = environment(), quiet = TRUE
    
  )
})

cat(unlist(gxs), sep = '\n')
```
</details>
