---
title: "Veteran Teacher Report - Demographics"
execute:
  echo: false
  message: false
  warning: false
format: 
  html:
    embed-resources: false
editor: visual
---

## Purpose

Provide demographics by school veteran status.

```{r}
#| echo: false
#| message: false
#| warning: false

## Housekeeping

## ---------------------------
## libraries
## ---------------------------
library(tidyverse)
library(kableExtra)
library(pwr)
library(knitr)

## ---------------------------
## directory paths
## ---------------------------

#see current directory
#getwd()

#set current directory
code_file_dir<-file.path("C:/Users/yjeff/Desktop/Community Schools/Teacher Retention Data","Analyses", "cs_teach_rent2","y3_data")

data_file_dir<-file.path("C:/Users/yjeff/Box/LAUSD TR Data Year 3")

## ---------------------------
## helper functions & strings
## ---------------------------

school_name_string<-c("all", "Elementary", "Middle/High School")

## ---------------------------
## load & inspect data
## ---------------------------

load(file.path(code_file_dir, "vet_combined_tbls.RData"))
load(file.path(code_file_dir, "demo_combined_tbls.RData"))
load(file.path(code_file_dir,'lausd_veteran.RData'))
load(file.path(code_file_dir,"veteran_percent_plots.RData"))

## Add Lists
#source(file.path(code_file_dir, "00_school_lists.R"))


```

# LAUSD Data

<details>

::: panel-tabset
#### Count
```{r}
veteran_status_wide_list[["count"]] %>% kable()
```

#### Percent
```{r}
veteran_status_wide_list[["percent"]] %>% kable()
```
:::

</details>


# Combined Version

# 5 Categories

Includes these categories: 

 - 0-3 years
 - 4-5 years
 - 6-10 years 
 - 11-15 years 
 - 15+ years

<details>
## All Teachers

<details>
```{r, echo = FALSE, results='asis'}
school_type_string<-names(vet_combined_tbls[["version1"]][["overall"]][["cs"]])

gxs<-lapply(1:length(school_type_string), function(x){
  
  school_type <- school_type_string[[x]]
  school_name <- school_name_string[[x]]
  
  count_tbl<-vet_combined_tbls[["version1"]][["overall"]][["cs"]][[school_type]][["teachers"]][["all"]][["count"]]
  
  percent_tbl<-vet_combined_tbls[["version1"]][["overall"]][["cs"]][[school_type]][["teachers"]][["all"]][["percent"]]

  graphs<-plots[["version1"]][[school_type]][["teachers"]][["all"]]
  
  knit_child(
    '_11.1_veteran_demographics - child.Rmd', envir = environment(), quiet = TRUE
    
  )
})

cat(unlist(gxs), sep = '\n')

```




## Teachers of color
<details>
```{r, echo = FALSE, results='asis'}
school_type_string<-names(vet_combined_tbls[["version1"]][["overall"]][["cs"]])

gxs<-lapply(1:length(school_type_string), function(x){
  
  school_type <- school_type_string[[x]]
  school_name <- school_name_string[[x]]
  
  count_tbl<-vet_combined_tbls[["version1"]][["overall"]][["cs"]][[school_type]][["teachers"]][["color"]][["count"]]
  
  percent_tbl<-vet_combined_tbls[["version1"]][["overall"]][["cs"]][[school_type]][["teachers"]][["color"]][["percent"]]

  graphs<-plots[["version1"]][[school_type]][["teachers"]][["color"]]
  
  knit_child(
    '_11.1_veteran_demographics - child.Rmd', envir = environment(), quiet = TRUE
    
  )
})

cat(unlist(gxs), sep = '\n')

```
</details>


</details>



# 2 Categories

Includes these categories: 

 - 0-5 years
 - 5+ years

<details>

## All Teachers
<details>
```{r, echo = FALSE, results='asis'}
school_type_string<-names(vet_combined_tbls[["version1"]][["overall"]][["cs"]])

gxs<-lapply(1:length(school_type_string), function(x){
  
  school_type <- school_type_string[[x]]
  school_name <- school_name_string[[x]]
  
  count_tbl<-vet_combined_tbls[["version2"]][["overall"]][["cs"]][[school_type]][["teachers"]][["all"]][["count"]]
  
  percent_tbl<-vet_combined_tbls[["version2"]][["overall"]][["cs"]][[school_type]][["teachers"]][["all"]][["percent"]]

  graphs<-plots[["version2"]][[school_type]][["teachers"]][["all"]]
  
  knit_child(
    '_11.2_veteran_demographics - child.Rmd', envir = environment(), quiet = TRUE
    
  )
})

cat(unlist(gxs), sep = '\n')

```


## Teachers of Color
<details>
```{r, echo = FALSE, results='asis'}
school_type_string<-names(vet_combined_tbls[["version1"]][["overall"]][["cs"]])

gxs<-lapply(1:length(school_type_string), function(x){
  
  school_type <- school_type_string[[x]]
  school_name <- school_name_string[[x]]
  
  count_tbl<-vet_combined_tbls[["version2"]][["overall"]][["cs"]][[school_type]][["teachers"]][["color"]][["count"]]
  
  percent_tbl<-vet_combined_tbls[["version2"]][["overall"]][["cs"]][[school_type]][["teachers"]][["color"]][["percent"]]

  graphs<-plots[["version2"]][[school_type]][["teachers"]][["color"]]
  
  knit_child(
    '_11.2_veteran_demographics - child.Rmd', envir = environment(), quiet = TRUE
    
  )
})

cat(unlist(gxs), sep = '\n')

```
</details>

</details>

# 3 Categories (Version 1) 
 
 NOTE: Teachers include In-Classroom & Out-of-Classroom Teachers
 
 Includes these categories: 

 - 0-3 years
 - 4-10 years
 - 10+ years
 
 
<details> 
 
## All Teachers
<details>
```{r, echo = FALSE, results='asis'}
school_type_string<-names(vet_combined_tbls[["version3"]][["overall"]][["cs"]])

gxs<-lapply(1:length(school_type_string), function(x){
  
  school_type <- school_type_string[[x]]
  school_name <- school_name_string[[x]]
  
  count_tbl<-vet_combined_tbls[["version3"]][["overall"]][["cs"]][[school_type]][["teachers"]][["all"]][["count"]]
  
  percent_tbl<-vet_combined_tbls[["version3"]][["overall"]][["cs"]][[school_type]][["teachers"]][["all"]][["percent"]]

  graphs<-plots[["version3"]][[school_type]][["teachers"]][["all"]]
  
  knit_child(
    '_11.3_veteran_demographics - child.Rmd', envir = environment(), quiet = TRUE
    
  )
})

cat(unlist(gxs), sep = '\n')

``` 
 

## Teachers of Color
<details>
```{r, echo = FALSE, results='asis'}
school_type_string<-names(vet_combined_tbls[["version1"]][["overall"]][["cs"]])

gxs<-lapply(1:length(school_type_string), function(x){
  
  school_type <- school_type_string[[x]]
  school_name <- school_name_string[[x]]
  
  count_tbl<-vet_combined_tbls[["version3"]][["overall"]][["cs"]][[school_type]][["teachers"]][["color"]][["count"]]
  
  percent_tbl<-vet_combined_tbls[["version3"]][["overall"]][["cs"]][[school_type]][["teachers"]][["color"]][["percent"]]

  graphs<-plots[["version3"]][[school_type]][["teachers"]][["color"]]
  
  knit_child(
    '_11.3_veteran_demographics - child.Rmd', envir = environment(), quiet = TRUE
    
  )
})

cat(unlist(gxs), sep = '\n')

``` 
</details>

</details>


# 3 Categories (Version 2) 
 
 NOTE: Only includes In-Classroom Teachers
 
 Includes these categories: 

 - 0-3 years
 - 4-10 years
 - 10+ years
 
 
<details> 
 
## All Teachers
<details>
```{r, echo = FALSE, results='asis'}
school_type_string<-names(vet_combined_tbls[["version4"]][["overall"]][["cs"]])

gxs<-lapply(1:length(school_type_string), function(x){
  
  school_type <- school_type_string[[x]]
  school_name <- school_name_string[[x]]
  
  count_tbl<-vet_combined_tbls[["version4"]][["overall"]][["cs"]][[school_type]][["teachers"]][["all"]][["count"]]
  
  percent_tbl<-vet_combined_tbls[["version4"]][["overall"]][["cs"]][[school_type]][["teachers"]][["all"]][["percent"]]

  graphs<-plots[["version4"]][[school_type]][["teachers"]][["all"]]
  
  knit_child(
    '_11.3_veteran_demographics - child.Rmd', envir = environment(), quiet = TRUE
    
  )
})

cat(unlist(gxs), sep = '\n')

``` 
 

## Teachers of Color
<details>
```{r, echo = FALSE, results='asis'}
school_type_string<-names(vet_combined_tbls[["version4"]][["overall"]][["cs"]])

gxs<-lapply(1:length(school_type_string), function(x){
  
  school_type <- school_type_string[[x]]
  school_name <- school_name_string[[x]]
  
  count_tbl<-vet_combined_tbls[["version4"]][["overall"]][["cs"]][[school_type]][["teachers"]][["color"]][["count"]]
  
  percent_tbl<-vet_combined_tbls[["version4"]][["overall"]][["cs"]][[school_type]][["teachers"]][["color"]][["percent"]]

  graphs<-plots[["version4"]][[school_type]][["teachers"]][["color"]]
  
  knit_child(
    '_11.3_veteran_demographics - child.Rmd', envir = environment(), quiet = TRUE
    
  )
})

cat(unlist(gxs), sep = '\n')

``` 
</details>

</details>

# Demographics - Percentage of Teachers of Color
<details>

```{r, echo = FALSE, results='asis'}
school_type_string<-names(demo_combined_tbls[["overall"]][["cs"]])

gxs<-lapply(1:length(school_type_string), function(x){
  
  school_type <- school_type_string[[x]]
  school_name <- school_name_string[[x]]
  
  count_tbl<-demo_combined_tbls[["overall"]][["cs"]][[school_type]][["teachers"]][["all"]][["count"]]
  
  percent_tbl<-demo_combined_tbls[["overall"]][["cs"]][[school_type]][["teachers"]][["all"]][["percent"]]

  graphs<-plots_demo[[school_type]][["teachers"]][["all"]]
  
  knit_child(
    '_11.3_veteran_demographics - child.Rmd', envir = environment(), quiet = TRUE
    
  )
})

cat(unlist(gxs), sep = '\n')

``` 


</details>

