---
title: "Veteran Teacher Report with LAUSD Data"
execute:
  echo: false
  message: false
  warning: false
format: 
  html:
    embed-resources: false
editor: visual
---

## Purpose

Provide demographics by school veteran status, which includes LAUSD Data.

```{r}
#| echo: false
#| message: false
#| warning: false

## Housekeeping

## ---------------------------
## libraries
## ---------------------------
library(tidyverse)
library(kableExtra)
library(pwr)
library(knitr)

## ---------------------------
## directory paths
## ---------------------------

#see current directory
#getwd()

#set current directory
code_file_dir<-file.path("C:/Users/yjeff/Desktop/Community Schools/Teacher Retention Data","Analyses", "cs_teach_rent2","y3_data")

data_file_dir<-file.path("C:/Users/yjeff/Box/LAUSD TR Data Year 3")

## ---------------------------
## helper functions & strings
## ---------------------------

school_name_string<-c("all", "Elementary", "Middle/High School")

## ---------------------------
## load & inspect data
## ---------------------------

load(file.path(code_file_dir, "vet_combined_tbls.RData"))
load(file.path(code_file_dir, "demo_combined_tbls.RData"))
load(file.path(code_file_dir,'lausd_veteran.RData'))
load(file.path(code_file_dir,"veteran_percent_plots.RData"))
load(file.path(code_file_dir, "lausd_vet_data.RData"))
load(file.path(code_file_dir, "lasud_cs_veteran_plots.RData"))

## Add Lists
#source(file.path(code_file_dir, "00_school_lists.R"))

```

# LAUSD Data

## LAUSD HR Data

<details>

```{r, echo = FALSE, results='asis'}

gxs<-lapply(1:1, function(x){
  
  knit_child(
    '_lausd_data - child.Rmd', envir = environment(), quiet = TRUE
    
  )
})

cat(unlist(gxs), sep = '\n')

```

</details>

## State Data

<details>

::: panel-tabset
#### Count

```{r}
veteran_status_wide_list[["count"]] %>% kable()
```

#### Percent

```{r}
veteran_status_wide_list[["percent"]] %>% kable()
```
:::

</details>

</details>

# BIPOC Demographic Data

## Derived BIPOC Veteran Teachers

::: panel-tabset
#### 2020-2021
```{r}
perc_tbl_bipoc[["2020_21"]] %>% kable()
```

In **2020-2021:**

Among **Elementary Teachers:** 

- `r perc_tbl_bipoc[["2020_21"]][1,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2020_21"]][1,12]`% are **BIPOC** 
 
Among **Secondary Teachers:** 
 
 - `r perc_tbl_bipoc[["2020_21"]][2,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2020_21"]][2,12]`% are **BIPOC** 

Among **Special Education Teachers:** 
 
 - `r perc_tbl_bipoc[["2020_21"]][3,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2020_21"]][3,12]`% are **BIPOC** 

Among **Teachers Overall:** 
 
 - `r perc_tbl_bipoc[["2020_21"]][4,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2020_21"]][4,12]`% are **BIPOC** 

#### 2021-2022
```{r}
perc_tbl_bipoc[["2021_22"]] %>% kable()

```

In **2021-2022:**

Among **Elementary Teachers:** 

- `r perc_tbl_bipoc[["2021_22"]][1,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2021_22"]][1,12]`% are **BIPOC** 
 
Among **Secondary Teachers:** 
 
 - `r perc_tbl_bipoc[["2021_22"]][2,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2021_22"]][2,12]`% are **BIPOC** 

Among **Special Education Teachers:** 
 
 - `r perc_tbl_bipoc[["2021_22"]][3,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2021_22"]][3,12]`% are **BIPOC** 

Among **Teachers Overall:** 
 
 - `r perc_tbl_bipoc[["2021_22"]][4,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2021_22"]][4,12]`% are **BIPOC** 

#### 2022-2023
```{r}
perc_tbl_bipoc[["2022_23"]] %>% kable()
```

In **2022-2023:**

Among **Elementary Teachers:** 

- `r perc_tbl_bipoc[["2022_23"]][1,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2022_23"]][1,12]`% are **BIPOC** 
 
Among **Secondary Teachers:** 
 
 - `r perc_tbl_bipoc[["2022_23"]][2,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2022_23"]][2,12]`% are **BIPOC** 

Among **Special Education Teachers:** 
 
 - `r perc_tbl_bipoc[["2022_23"]][3,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2022_23"]][3,12]`% are **BIPOC** 

Among **Teachers Overall:** 
 
 - `r perc_tbl_bipoc[["2022_23"]][4,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2022_23"]][4,12]`% are **BIPOC** 



#### 2023-2024
```{r}
perc_tbl_bipoc[["2023_24"]] %>% kable()
```

In **2023-2024:**

Among **Elementary Teachers:** 

- `r perc_tbl_bipoc[["2023_24"]][1,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2023_24"]][1,12]`% are **BIPOC** 
 
Among **Secondary Teachers:** 
 
 - `r perc_tbl_bipoc[["2023_24"]][2,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2023_24"]][2,12]`% are **BIPOC** 

Among **Special Education Teachers:** 
 
 - `r perc_tbl_bipoc[["2023_24"]][3,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2023_24"]][3,12]`% are **BIPOC** 

Among **Teachers Overall:** 
 
 - `r perc_tbl_bipoc[["2023_24"]][4,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2023_24"]][4,12]`% are **BIPOC** 


#### 2024-2025
```{r}
perc_tbl_bipoc[["2024_25"]] %>% kable()
```

In **2024-2025:**

Among **Elementary Teachers:** 

- `r perc_tbl_bipoc[["2024_25"]][1,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2024_25"]][1,12]`% are **BIPOC** 
 
Among **Secondary Teachers:** 
 
 - `r perc_tbl_bipoc[["2024_25"]][2,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2024_25"]][2,12]`% are **BIPOC** 

Among **Special Education Teachers:** 
 
 - `r perc_tbl_bipoc[["2024_25"]][3,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2024_25"]][3,12]`% are **BIPOC** 

Among **Teachers Overall:** 
 
 - `r perc_tbl_bipoc[["2024_25"]][4,11]`% are **BIPOC & have 10+ years of teaching experience**, `r perc_tbl_bipoc[["2024_25"]][4,12]`% are **BIPOC** 

:::


## Process
<details>

### Formulas

<details>

We used the following formulas to calculate the BIPOC values:

**Calculate the Number of BIPOC Veteran Teachers**
$$ 
\text{(Total Number of Veteran Teachers)} \times \text{(Proportion BIPOC)}
$$
$$
= \text{Number of BIPOC Veteran Teachers} 
$$



 
For example, below is a more precise formula to calculate the **number of BIPOC teachers with 10+ years of experience**. 

$$ 
\begin{aligned}
\text{(Total Number of Teachers with over 10+ years of experience)} 
\times \text{(Proportion BIPOC)} \\ 
= \text{Number of BIPOC Teachers with over 10 years of experience} 
\end{aligned}
$$

**Calculate Percent BIPOC Veteran Teachers**

$$
\frac{\text {Number of BIPOC Veteran Teachers}} {\text {Number of All Teachers}} = 
\text{Percent of BIPOC Veteran Teachers}
$$
</details>

### Number of BIPOC Teachers by Veteran Status

To determine the number of BIPOC teachers by veteran status, we first determined the percentage of BIPOC teachers in the sample (see tables below).

::: panel-tabset
#### 2020-2021
```{r}
bipoc_calculated_lausd_data[["2020_21"]] %>% kable()
```

#### 2021-2022
```{r}
bipoc_calculated_lausd_data[["2021_22"]] %>% kable()
```

#### 2022-2023
```{r}
bipoc_calculated_lausd_data[["2022_23"]] %>% kable()
```

#### 2023-2024
```{r}
bipoc_calculated_lausd_data[["2023_24"]] %>% kable()
```

#### 2024-2025
```{r}
bipoc_calculated_lausd_data[["2024_25"]] %>% kable()
```
:::

Using the first formula, we then calculated the number of BIPOC teachers by veteran status.

::: panel-tabset
#### 2020-2021
```{r}
bipoc_count_tbl[["tv_2020_21"]] %>% kable()
```

#### 2021-2022
```{r}
bipoc_count_tbl[["tv_2021_22"]] %>% kable()
```

#### 2022-2023
```{r}
bipoc_count_tbl[["tv_2022_23"]]%>% kable()
```

#### 2023-2024
```{r}
bipoc_count_tbl[["tv_2023_24"]]%>% kable()
```

#### 2024-2025
```{r}
bipoc_count_tbl[["tv_2024_25"]]%>% kable()
```
:::

With this table, we then use the second formula to determine the percentage of BIPOC veteran teachers (see **Derived BIPOC Veteran Teachers** section).


</details>
</details>

# Percentage Plots of BIPOC Veteran Teachers

NOTE: Only includes In-Classroom Teachers who are teachers of color, and have over 10 years for experience.


## Overall

<details>

::: panel-tabset

### All
```{r}
update_plots_demo[["original_sch"]][["all"]][["teachers"]][["all"]][["10+ years"]] 
```

### Elementary
```{r}
update_plots_demo[["original_sch"]][["elem"]][["teachers"]][["all"]][["10+ years"]] 
```

### Secondary
```{r}
update_plots_demo[["original_sch"]][["mid_hi"]][["teachers"]][["all"]][["10+ years"]]
```

:::

</details>

## Percentage Plots of BIPOC Veteran Teachers by Cohort
<details>
::: panel-tabset

### Cohort 1
```{r}
update_plot_tbls_demo_cohort[["cohort_sch"]][["cohort1"]][["teachers"]][["10+ years"]]
```

### Cohort 2
```{r}
update_plot_tbls_demo_cohort[["cohort_sch"]][["cohort2"]][["teachers"]][["10+ years"]]
```

### Cohort 3
```{r}
update_plot_tbls_demo_cohort[["cohort_sch"]][["cohort3"]][["teachers"]][["10+ years"]]
```

:::

</details>